Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-27 proposal/prop.tex
prop.tex \subsection{Measuring Probabilities: Buffon's Needle Problem} Add citation...

In the previous example, we assumed the probability~$\pmeas(E)$ of
each event~$E$ is known a priori. In reality, although each event is
assumed to have a probability, the exact value of $\pmeas(E)$ may not
be known. According to the \emph{frequency interpretation of
  probability} (which we will revisit when moving to the quantum
case), to determine the probability of an event, we run $N$
independent trials which gives us an approximation of the (assumed)
``true'' or ``real'' probability. Let $x_{i}$ be 1 or 0 depending on
whether the event~$E$ occurs in the $i$-th trial or not, then
$\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$ by
the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$ with the
probability converging to one as $N$ goes to infinity, i.e.,
\[
\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sideset{}{_{i=1}^{N}}\sum x_{i}\right|<\epsilon\right)=1\textrm{ .}
\]
This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

>>>>

In the previous example, we assumed the probability~$\pmeas(E)$ of
each event~$E$ is known a priori. In reality, although each event is
assumed to have a probability, the exact value of $\pmeas(E)$ may not
be known. According to the \emph{frequency interpretation of
  probability} (which we will revisit when moving to the quantum
case)~\cite{Venn1876,Hajek2012}, 
to determine the probability of an event, we run $N$
independent trials which gives us an approximation of the (assumed)
``true'' or ``real'' probability. Let $x_{i}$ be 1 or 0 depending on
whether the event~$E$ occurs in the $i$-th trial or not, then
$\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$ by
the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$ with the
probability converging to one as $N$ goes to infinity, i.e.,
\[
\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sideset{}{_{i=1}^{N}}\sum x_{i}\right|<\epsilon\right)=1\textrm{ .}
\]
This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
